---
title: "Colourism in the East and South Asian Beauty Markets"
format: pdf
author: "Laura Lee-Chu"
abstract: "The cosmetic industry has been instrumental in perpetuating and exacerbating colorism across Asia. This study employs data from The Pudding to analyze the relationship between foundation shades offered by popular makeup brands and the range of skin tones in Japan and India. Based on the findings, there is a noticeable similarity in the distribution of lightness among foundation shades in both Indian and Japanese cosmetics. The findings reveal that while certain Japanese beauty brands offer foundation shades that are suitable for East Asian skin tones, the range of available colors is biased towards lighter skin tones. Conversely, foundation shades available in India are considerably brighter than the natural skin tone of South Asians. The results demonstrate the influence of colorism and the pursuit of proximity to whiteness."
date: today
date-format: long
editor: visual
toc: TRUE
number-sections: TRUE
bibliography: references.bib
thanks: "Code and data supporting this analysis is available at: "
---

```{r}
#| messages: false
#| echo: false
#| warning: false
#| output: false

#### Preamble ####
# Title:
# Author: Laura Lee-Chu
# Email: 
# Date: 16 March 2023

#### Work space set-up ####
# Define required libraries 
library(lubridate)
library(tidyverse)
library(dplyr)
library(knitr)
library(janitor)
library(scales)
library(RColorBrewer)
library(ggplot2)
library(kableExtra)
library(here)
library(readr)

# Fetching the shade range data 
cleanshades <- readr::read_csv(here::here("inputs/data/clean/cleanshades.csv"), show_col_types = FALSE)

lightnessrange <- readr::read_csv(here::here("inputs/data/clean/lightnessrange.csv"), show_col_types = FALSE)
```



```{r}
#| messages: false
#| echo: false
#| warning: false


#total number of shade range 
lightnessrange |>
  tabyl(group, light_range) |>
  adorn_totals("col") 
  
```
```{r}
#| messages: false
#| echo: false
#| warning: false

#India 

lightnessrange |>
  filter(group == 'India') |>
  ggplot(aes(x = brand, y = L)) +
    geom_dotplot(binaxis='y', 
               stackdir='center',
               binwidth = 0.7, 
               fill = "#ebb08a")  +
  scale_y_continuous(breaks=seq(0, 100, 5)) +
  theme_minimal() +
  coord_flip() +
  labs(
    y = "Lightness Value", 
    x = "Best Selling Indian Foundation Brands"
  )
    

```

```{r}
#| messages: false
#| echo: false
#| warning: false

#japan

lightnessrange |>
  filter(group == 'Japan') |>
  ggplot(aes(x = brand, y = L)) +
    geom_dotplot(binaxis='y', 
               stackdir='center',
               binwidth = 0.5, 
               fill = "#e8b793") +
  scale_y_continuous(breaks=seq(0, 100, 5)) +
  theme_minimal() +
  coord_flip() +
  labs(
    y = "Lightness Value", 
    x = " Bestselling Japanese Foundation Brands"
  )
    


```







```{r}
#| messages: false
#| echo: false
#| warning: false


#india & Japan

# lightnessrange |>
#   nrow()




lightnessrange |>
  ggplot(aes(x = light_range, fill = group)) +
  geom_bar() +
  theme_minimal() +
  labs(
    x = "Lightness Range",
    y = "Number of Foundation Shades"
  )

```







```{r}
#| messages: false
#| echo: false
#| warning: false

#japan

lightnessrange |>
  filter(group == 'Japan') |>
  ggplot(aes(x = H, y = L)) +
    geom_point(fill = "#e8b793") +
  # scale_x_continuous(breaks=seq(22, 25, 0.1)) +
  theme_minimal() +
  labs(
    y = "Lightness Value", 
    x = "Hue"
  )
    
```





```{r}

install.packages("ggpubr")
install.packages("broom") 
install.packages("AICcmodavg") 

library(ggplot2)
library(ggpubr)
library(tidyverse)
library(broom)
library(AICcmodavg)

one.way <- aov(group ~ L, data = lightnessrange)
summary(one.way)

```

















\newpage



**Data Acknowledgement**



**Resources Acknowledgment**

The primary tool used to analyse data in this paper is R, an open-source statistical programming language [@cite_tool_r]. The paper also uses a number of R packages, including: dplyr [@cite_tool_dplyr], foreign [@cite_tool_foreign], ggplot2 [@cite_tool_ggplot2], here [@cite_tool_here], janitor [@cite_tool_janitor], kableExtra [@cite_tool_kableextra], knitr [@cite_tool_knitr], lubridate [@cite_tool_lubridate], readr [@cite_tool_readr], RColorBrewer [@cite_tool_rcolorbrewer], scales [@cite_tool_scales], and tidyverse [@cite_tool_tidyverse]. \newpage

## Appendix


\newpage

## References

<!-- Comment required to show references as a numbered section -->
